---
title: "Crime Analyst Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(sf)
library(lubridate)
library(sp)
library(stringr)
```


ideas: Track Illegal firearm seizures with economy?

Interesting Datasets:
Right-of-Way Permits and Traffic-Obstruction Permits
Pittsburgh American Community Survey 2015, School Enrollment
City Owned Publicly Available Properties
City Revenues and Expenses
Condemned and Dead-End Properties
Pittsburgh PLI/DOMI Violations Report
Police Incident Blotter (Archive)

Police Community Outreach

Police Officer Training


```{r}
arrestData<-read.csv("/Users/4victoria98/Downloads/Crime Analyst/arrestData.csv")
View(arrestData)
```


```{r}
municipalities<-st_read("/Users/4victoria98/Downloads/Capstone/Re_ Pittsburgh Park Conservancy Meeting/LandRecords_LANDRECORDS_OWNER_Municipalities.shp")
```
```{r}
View(municipalities)
```



```{r}
pittsburgh<-municipalities%>%filter(NAME=="PITTSBURGH")
pittsburghT <- st_transform(pittsburgh, "NAD83")
shpData <- arrestData%>%filter(!is.na(X)&!is.na(Y))
lat<-shpData$Y
long<-shpData$X
coordinates(shpData)=c("X","Y")
proj4string(shpData)<- CRS("+proj=longlat +datum=NAD83")
```

```{r}
sfData<-st_as_sf(shpData)

sfDataPitt<- sfData%>%sf::st_filter(pittsburghT)

```


```{r}

vectX<-arrestData$X
vectY<-arrestData$Y
ggplot(data=pittsburghT)+geom_sf(fill="forestgreen")+
    geom_sf(data = sfDataPitt,color="blue", alpha=.2, size = 1 )+
    coord_sf(xlim = c(-80.1, -79.85), ylim = c(40.35, 40.51), expand = FALSE)+theme_bw()
    #    shape = 23, fill = "darkred") 
```
```{r}
sfDataPitt$date<-ymd(substr(sfDataPitt$ARRESTTIME, 1, 10))
sfDataPitt$hour<-as.numeric(substr(sfDataPitt$ARRESTTIME, 12, 13))
sfDataPitt$minute<-as.numeric(substr(sfDataPitt$ARRESTTIME, 15, 16))
```

```{r}
min(sfDataPitt$date)
max(sfDataPitt$date)
```


```{r}
ggplot(sfDataPitt)+geom_bar(aes(x=hour))+labs(title="Total Number of Arrests Per Hour from October 1998-April 2023") +theme_bw()
```


```{r}
sum(crimeData$hour==16)/ nrow(crimeData) + sum(crimeData$hour==17)/ nrow(crimeData) +sum(crimeData$hour==18)/ nrow(crimeData) +sum(crimeData$hour==1)/ nrow(crimeData)+sum(crimeData$hour==2)/ nrow(crimeData)+sum(crimeData$hour==4)/ nrow(crimeData) + sum(crimeData$hour==5)/ nrow(crimeData) +sum(crimeData$hour==6)/ nrow(crimeData)+ sum(crimeData$hour==7)/ nrow(crimeData)
```


```{r}
mean(crimeData$Black)
mean(crimeData$White)
mean(crimeData$Other)
mean(crimeData$Minor, na.rm = TRUE)
mean(crimeData$Elderly, na.rm = TRUE)

mean(crimeData$YA, na.rm = TRUE) + mean(crimeData$MA, na.rm = TRUE)

mean(crimeData$YA, na.rm = TRUE) 
mean(crimeData$MA, na.rm = TRUE)

#sum(is.na(crimeData$Minor))
```



```{r}
fred<-read_csv("/Users/4victoria98/Downloads/Crime Analyst/GDPC1.csv")
View(fred)
```

```{r}
int.rates<-read_csv("/Users/4victoria98/Downloads/Crime Analyst/INTDSRUSM193N.csv")
#View(int.rates)
```

```{r}
colnames(int.rates)<-c("Date", "rate")
colnames(fred)<-c("Date", "GDP")

plot1<-ggplot(sfDataPitt)+geom_bar(aes(x=date))+labs(title="Total Number of Crimes by Date from October 1998-April 2023") +theme_bw() 
plot2<-plot1+geom_line(data=int.rates, aes(x=Date, y=rate))+expand_limits(y=c(0,6))
plot2
```

#Add interest rates to crime data
```{r}
sfDataPitt$yearmonth<-ymd(paste(substring(sfDataPitt$date, 1,7), "-01", sep=""))
colnames(sfDataPitt)[19]="Date"

crimeData<-merge(sfDataPitt, int.rates, by="Date", all.x=TRUE)
crimeData<-merge(crimeData, fred, by="Date", all.x=TRUE)

crimeData$Code<-word(crimeData$OFFENSES, 1)
```



```{r}
crimes.byDate<-as.data.frame(table(crimeData$Date))
crimes.byDate

crimes.byOffense<-as.data.frame(table(crimeData$INCIDENTNEIGHBORHOOD))
crimes.byOffense
```
Rob
Assault
Voluntary Manslaughter
```{r}
mur<-grepl("Voluntary Manslaughter", crimeData$OFFENSES)

for(i in 1:nrow(crimeData)){
  if(mur[i]==TRUE)
    print(crimeData$OFFENSES[i])
}
```


#We see from this table that Data wasn't being reliably recorded before September of 2016

```{r}
crimes.byOffense<-crimes.byOffense%>%filter(Freq>20)
crimes.byOffense
```

```{r}
crimeData<-crimeData%>%filter(Date>=ymd("2016-09-01"))
ggplot(crimeData)+geom_bar(aes(x=date, fill=RACE))+labs(title="Total Number of Crimes by Race from October 1998-April 2023") +theme_bw() 
```



```{r}
crimeData$Year<-year(crimeData$Date)
crimeData$Black<-ifelse(crimeData$RACE=="B",1,0)
crimeData$White<-ifelse(crimeData$RACE=="W",1,0)
crimeData$Other<-ifelse(crimeData$RACE!="W"&crimeData$RACE!="B",1,0)

crimeData$Minor<-ifelse(crimeData$AGE<18,1,0)
crimeData$YA<-ifelse(crimeData$AGE>18&crimeData$AGE<=30,1,0)
crimeData$MA<-ifelse(crimeData$AGE<=65&crimeData$AGE>30,1,0)
crimeData$Elderly<-ifelse(crimeData$AGE>65,1,0)
crimeData$Arrest<-1
```

```{r}
more.than2017<-crimeData%>%filter(Year>2016)
agged.sum.data<-aggregate(cbind(Arrest, ViolentCrime)~Year, data=more.than2017, sum)
agged.mean.data<-aggregate(cbind(Black, White, Other, Minor,YA,MA,Elderly, ViolentCrime)~Year, data=more.than2017, mean)
agged.data<-merge(agged.sum.data, agged.mean.data, by="Year")

#colnames(agged.data)<-c("Year","Total Arrests", "% Black", "% White", "% Other", "% < 18", "% 18-30", "% 31-65", "% 65 +")

agged.data
```

```{r}
agged.sum.data<-aggregate(cbind(Zone1, Zone2, Zone3, Zone4, Zone5, Zone6)~Year, data=more.than2017, mean)
#colnames(agged.data2)<-c("Year","Total Arrests", "% Black", "% White", "% Other", "% < 18", "% 18-30", "% 31-65", "% 65 +")

agged.sum.data
```
```{r}
zone<-1:6
means<-c(mean(crimeData$Zone1),mean(crimeData$Zone2),mean(crimeData$Zone3),mean(crimeData$Zone4),mean(crimeData$Zone5),mean(crimeData$Zone6))
zone.means<-as.data.frame(matrix(data=c(zone, round(means*100, digits = 0)), ncol = 2))

colnames(zone.means)<-c("Zone", "Percent of Arrests")
zone.means

```

```{r}
ggplot(zone.means, aes(x=Zone, y=`Percent of Arrests`))+geom_col()+labs(y="Percent of Total Arrests", x="Zone", title = "What Percentage of Municipal Arrests is Each Zone Accounting for?") + theme_bw()
```

```{r}
mean_inc<-c(mean(zone1inc_F2$Income),mean(zone2inc_F2$Income),mean(zone3inc_F2$Income),mean(zone4inc_F2$Income),mean(zone5inc_F2$Income),mean(zone6inc_F2$Income))
mean_pop<-c(mean(zone1inc_F2$Population),mean(zone2inc_F2$Population),mean(zone3inc_F2$Population),mean(zone4inc_F2$Population),mean(zone5inc_F2$Population),mean(zone6inc_F2$Population))

zone.chars<-as.data.frame(matrix(data=c(zone, round(mean_inc, digits = 0), round(mean_pop, digits = 0)), ncol = 3))

colnames(zone.chars)<-c("Zone", "Mean Tract Income", "Mean Tract Population")
zone.chars
```
```{r}
write_csv(zone.chars, "/Users/4victoria98/Downloads/zone_chars.csv")
```


#NOTES: NUMBER OF ARRESTS HAS BEEN FALLING STEADILY SINCE 2017. ARRESTS IN 2022 WERE JUST LESS THAN 1/2 OF ARRESTS IN 2017 (48.69%)
        CONVERSELY, THE PROPORTION OF ARRESTS THAT HAVE BEEN OF BLACK CITIZENS HAS RISEN BY 18.79%
        
```{r}
write_csv(agged.data, "/Users/4victoria98/Downloads/sum.stats.csv")
```

```{r}
agged.data
```


```{r}
agged.data<-agged.data%>%filter(Year>2016&Year<2023)

summary(lm(Black.x~Year, agged.data))
summary(lm(White.x~Year, agged.data))
```

#Words for Violent crime:
  #Rob
Assault
Voluntary Manslaughter
  
```{r}
crimeData$ViolentCrime<-ifelse(grepl("Rob", crimeData$OFFENSES)|grepl("Assault", crimeData$OFFENSES)| grepl("Voluntary Manslaughter", crimeData$OFFENSES),1,0)
```

```{r}
community.engagement<-read_csv("/Users/4victoria98/Downloads/Crime Analyst/Community_Outreach.csv")
```

```{r}
police_zones<-st_read("/Users/4victoria98/Downloads/Crime Analyst/Police_Zones/Police_Zones.shp")
```

```{r}
ggplot(data=police_zones)+geom_sf(aes(fill=as.factor(zone)))

police_zonesT <- st_transform(police_zones, "NAD83")
ggplot(data=police_zonesT)+geom_sf(aes(fill=as.factor(zone)))

```
```{r}
library(tidycensus)

# list of variables to be extracted

demographic_vars <- c(
Population = "B02001_001",
Hispanic = "B03002_013",
White = "B02001_002",
Black = "B02009_001",
Asian = "B02015_001",
Median_Inc = "B06011_001"
)

# access the census data

Allegheny <- get_acs(geography = "tract", 
              variables = demographic_vars, 
              state = "PA", 
              county = "ALLEGHENY",
              survey = "acs5",
              year = 2020)


# Make this badboy a dataframe

Allegheny <- as.data.frame(Allegheny)

```

```{r}
library(tigris)
Allegheny_Tracts <- tracts("PA", "Allegheny", year= 2020)


Black <- subset(Allegheny, variable == "Black") %>% select(GEOID, estimate)
Black <- setNames(Black, c("GEOID","Black"))

Population <- subset(Allegheny, variable == "Population") %>% select(GEOID, estimate)
Population <- setNames(Population, c("GEOID","Population"))

Income <- subset(Allegheny, variable == "Median_Inc") %>% select(GEOID, estimate)
Income <- setNames(Income, c("GEOID","Income"))

# now use the SF package to merge these things back to the tract map based on GEOID

Combined <- geo_join (Allegheny_Tracts, Black, "GEOID", "GEOID" )
Combined <- geo_join (Combined, Population, "GEOID", "GEOID" )
Combined <- geo_join (Combined, Income, "GEOID", "GEOID" )

# generate Percent black
Combined$Pct_Black <- Combined$Black/Combined$Population

# get rid of NA
Combined[is.na(Combined)] <- 0

```

```{r}
Combined %>%
  ggplot(aes(x = Pct_Black, y = Income)) + 
  geom_point() +
  geom_smooth(se=TRUE, method="lm", span=.5, formula=y ~ poly(x, 3, raw=TRUE),colour="red")
```
```{r}
# Median Income

ggplot(Combined, aes(fill = Income))+
  geom_sf(, colour = NA) +
  scale_fill_viridis_c(option = "magma",begin = 0, end = .99)  + 
  ggtitle("Median Income in Tract")
```
ggplot(data=pittsburghT)+geom_sf(fill="forestgreen")+
    geom_sf(data = sfDataPitt,color="blue", alpha=.2, size = 1 )+
    coord_sf(xlim = c(-80.1, -79.85), ylim = c(40.35, 40.51), expand = FALSE)+theme_bw()
    #    shape = 23, fill = "darkred") 

```{r}
pittsburgh_census <- st_transform(Combined, "NAD83")

pittsburgh_census1<- pittsburgh_census%>%sf::st_filter(pittsburghT,.predicate = st_within)

pittsburgh_census<- pittsburgh_census%>%sf::st_filter(pittsburghT)

ggplot(data=pittsburghT)+
  geom_sf(fill="green", color=NA) +geom_sf(data=pittsburgh_census, aes(fill=Income), alpha=.4)+scale_fill_viridis_c(option = "magma",begin = 0, end = .99)  + ggtitle("Median Income in Tract")

ggplot(data=pittsburghT)+
  geom_sf(fill="green", color=NA) +geom_sf(data=pittsburgh_census1, aes(fill=Income), alpha=.4)+scale_fill_viridis_c(option = "magma",begin = 0, end = .99)  + ggtitle("Median Income in Tract")

```
```{r}
zone1<-police_zonesT%>%filter(zone==1)
zone1inc<-pittsburgh_census%>%sf::st_filter(zone1) 
ggplot(data=zone1)+
  geom_sf(fill="green", color=NA) +geom_sf(data=zone1inc, aes(fill=Income), alpha=.4)+scale_fill_viridis_c(option = "magma",begin = 0, end = .99)  + ggtitle("Median Income in Tract")
```



#TAKE OUT TRACTS WITH POPULATION 0 AND LOOK AGAIN
```{r}
zone1<-police_zonesT%>%filter(zone==1)
pittsburgh_census$id<-1:nrow(pittsburgh_census)
pittsburgh_census$id<-as.character(pittsburgh_census$id)


zone1inc<-pittsburgh_census%>%sf::st_filter(zone1) 

zone1inc_F<-zone1inc%>%filter(Population>0) 

zone1inc_F2<-zone1inc_F%>% filter(!id%in%c("136","137","97","9","90","8", "96"))

ggplot(data=zone1)+
  geom_sf(color="red", fill="green") +geom_sf(data=zone1inc_F, aes(fill=id), alpha=.4)#+scale_fill_viridis_c(option = "magma",begin = 0, end = .99)  + ggtitle("Median Income in Tract")

ggplot(data=zone1)+
  geom_sf(fill="green",color=NA) +geom_sf(data=zone1inc_F2, aes(fill=id), alpha=.4)#+scale_fill_viridis_c(option = "magma",begin = 0, end = .99)  + ggtitle("Median Income in Tract")

```

```{r}
zone2<-police_zonesT%>%filter(zone==2)


zone2inc<-pittsburgh_census%>%sf::st_filter(zone2) 

zone2inc_F<-zone2inc%>%filter(Population>0) 

zone2inc_F2<-zone2inc_F%>% filter(!id%in%c("141", "69","113","57","36","37","70","162"))  #,"97","9","90","8", "96")) NOT: 31, 35, 148

ggplot(data=zone2)+
  geom_sf(color="red", fill="green") +geom_sf(data=zone2inc_F, aes(fill=id), alpha=.4)#+scale_fill_viridis_c(option = "magma",begin = 0, end = .99)  + ggtitle("Median Income in Tract")

ggplot(data=zone2)+
  geom_sf(fill=NA,color=NA) +geom_sf(data=zone2inc_F2, aes(fill=id), alpha=.4)#+scale_fill_viridis_c(option = "magma",begin = 0, end = .99)  + ggtitle("Median Income in Tract")

```

```{r}
ggplot(data=zone3)+
  geom_sf(color="red", fill="green") +geom_sf(data=zone3inc_F, aes(fill=id), alpha=.4)#+scale_fill_viridis_c(option = "magma",begin = 0, end = .99)  + ggtitle("Median Income in Tract")
```

```{r}
zone3<-police_zonesT%>%filter(zone==3)


zone3inc<-pittsburgh_census%>%sf::st_filter(zone3) 

zone3inc_F<-zone3inc%>%filter(Population>0) 

ggplot(data=zone3)+
 geom_sf(fill="green",color=NA) +geom_sf(data=zone3inc_F2, aes(fill=id), alpha=.4)#+scale_fill_viridis_c(option = "magma",begin = 0, end = .99)  + ggtitle("Median Income in Tract")

zone3inc_F2<-zone3inc_F%>% filter(!id%in%c("159", "161","153", "151","77","49","27","47","48","61","80","124")) #NOT: 143, 144, 134


ggplot(data=zone3)+
 geom_sf(fill=NA,color=NA) +geom_sf(data=zone3inc_F2, aes(fill=id), alpha=.4)#+scale_fill_viridis_c(option = "magma",begin = 0, end = .99)  + ggtitle("Median Income in Tract")

```

```{r}
zone4<-police_zonesT%>%filter(zone==4)


zone4inc<-pittsburgh_census%>%sf::st_filter(zone4) 

zone4inc_F<-zone4inc%>%filter(Population>0) 

ggplot(data=zone4)+
 geom_sf(fill="green",color=NA) +geom_sf(data=zone4inc_F2, aes(fill=id), alpha=.4)#+scale_fill_viridis_c(option = "magma",begin = 0, end = .99)  + ggtitle("Median Income in Tract")

zone4inc_F2<-zone4inc_F%>% filter(!id%in%c("155","92","93","91","89","10","104","108","151", "5", "41", "163","164","68", "31","29","166","6","74","82","11","83","3")) #NOT: 85, 88, 141,145, 57, 67, 30,32,33,34, 26,23


ggplot(data=zone4)+
 geom_sf(fill=NA,color=NA) +geom_sf(data=zone4inc_F2, aes(fill=id), alpha=.4)#+scale_fill_viridis_c(option = "magma",begin = 0, end = .99)  + ggtitle("Median Income in Tract")

```

for(i in 1:nrow(pittsburgh_census)){
 print(lengths(st_intersects(crimeData$geometry[1], pittsburgh_census$geometry[i])))
  print(st_intersects(crimeData$geometry[1], pittsburgh_census$geometry[i]))
  print(i)
}
nrow(crimeData)
```{r}
#View(crimeData)
length(st_intersects(crimeData$geometry[1], pittsburgh_census$geometry[i])[[1]])
st_intersects(crimeData$geometry[1], pittsburgh_census$geometry[20])
length(st_intersects(crimeData$geometry[1], pittsburgh_census$geometry[20])[[1]])

crimeData$tract_income<-0
crimeData$tractPop<-0
crimeData$tractID<-0
crimeData$pct_black<-0

crime<-1

for(crime in 1:100){
  for(i in 1:nrow(pittsburgh_census)){
    if(lengths(st_intersects(crimeData$geometry[crime], pittsburgh_census$geometry[i]))==1){
      crimeData[crime,33]<-pittsburgh_census$Income[i]
      crimeData[crime,34]<-pittsburgh_census$Population[i]
      crimeData[crime,35]<-pittsburgh_census$id[i]
      crimeData[crime,36]<-pittsburgh_census$Pct_Black[i]
    }
  }
  print(crime)
}
```


```{r}
zone5<-police_zonesT%>%filter(zone==5)


zone5inc<-pittsburgh_census%>%sf::st_filter(zone5) 

zone5inc_F<-zone5inc%>%filter(Population>0) 

ggplot(data=zone5)+
 geom_sf(fill="green",color=NA) +geom_sf(data=zone5inc_F2, aes(fill=id), alpha=.4)#+scale_fill_viridis_c(option = "magma",begin = 0, end = .99)  + ggtitle("Median Income in Tract")

zone5inc_F2<-zone5inc_F%>% filter(!id%in%c("142", "94","38","22","146","41", "167","122","42","92","35","57")) #NOT: 14, 131,3, 29, 12,13


ggplot(data=zone5)+
 geom_sf(fill=NA,color=NA) +geom_sf(data=zone5inc_F2, aes(fill=id), alpha=.4)#+scale_fill_viridis_c(option = "magma",begin = 0, end = .99)  + ggtitle("Median Income in Tract")

```

```{r}
ggplot(data=zone6)+
 geom_sf(fill="green",color=NA) 
```


```{r}
zone6<-police_zonesT%>%filter(zone==6)


zone6inc<-pittsburgh_census%>%sf::st_filter(zone6) 

zone6inc_F<-zone6inc%>%filter(Population>0) 

ggplot(data=zone6)+
 geom_sf(fill="green",color=NA) +geom_sf(data=zone6inc_F2, aes(fill=id), alpha=.4)#+scale_fill_viridis_c(option = "magma",begin = 0, end = .99)  + ggtitle("Median Income in Tract")

zone6inc_F2<-zone6inc_F%>% filter(!id%in%c("18","21","144","156","25","78","129","54","50","51","52","56","58","60","46","53","55","48","118","134","76", "79","87")) #NOT:160, 124,59


ggplot(data=zone6)+
 geom_sf(fill=NA,color=NA) +geom_sf(data=zone6inc_F2, aes(fill=id), alpha=.4)#+scale_fill_viridis_c(option = "magma",begin = 0, end = .99)  + ggtitle("Median Income in Tract")

```
```{r}

```



```{r}
income_data<-rbind(zone1inc_F2,zone2inc_F2,zone3inc_F2,zone4inc_F2,zone5inc_F2,zone6inc_F2)
police_zonesT$char_zone<-as.character(police_zonesT$zone)

annotation <- data.frame(
   x = c(-80.02, -79.97,-79.99, -79.927, -79.918, -80.045),
   y = c(40.47,40.455, 40.425, 40.435, 40.474, 40.444),
   label = c("Zone 1", "Zone 2", "Zone 3", "Zone 4", "Zone 5", "Zone 6")
)

ggplot()+
 geom_sf(data=income_data,color="grey", aes(fill=Income), alpha=.7)+geom_sf(data=police_zonesT, color="black", fill=NA)+theme_bw()+geom_text(data=annotation, aes(x=x, y = y, label=label))+labs(title="Median Income in US Census Tracts Across Police Zones",x="",y="")

```

```{r}
crimeData$Zone1<-ifelse(crimeData$INCIDENTZONE==1,1,0)
crimeData$Zone2<-ifelse(crimeData$INCIDENTZONE==2,1,0)
crimeData$Zone3<-ifelse(crimeData$INCIDENTZONE==3,1,0)
crimeData$Zone4<-ifelse(crimeData$INCIDENTZONE==4,1,0)
crimeData$Zone5<-ifelse(crimeData$INCIDENTZONE==5,1,0)
crimeData$Zone6<-ifelse(crimeData$INCIDENTZONE==6,1,0)

agged.sum.data1<-aggregate(cbind(Black, White, Other, Arrest, Zone1,Zone2,Zone3,Zone4,Zone5,Zone6, ViolentCrime)~date, data=crimeData, sum)
agged.mean.data1<-aggregate(cbind(Black, White, Other, Minor,YA,MA,Elderly, ViolentCrime)~date, data=crimeData, mean)
agged.data1<-merge(agged.mean.data1, agged.sum.data1, by="date")
agged.data1

agged.data1$Year<-year(agged.data1$date)
agged.data1$Month<-month(agged.data1$date)
agged.data1$wday<-wday(agged.data1$date, label=TRUE)

agged.data1
```

```{r}
tw17plus<-agged.data1%>%filter(Year>2016&Year<2023)
summary(lm(ViolentCrime.y~Year, agged.data1))

tw17plusyr<-agged.data%>%filter(Year>2016&Year<2023)
summary(lm(ViolentCrime.x~Year, agged.data))
```



```{r}
sum(agged.data1$Zone1)
sum(agged.data1$Zone2)
sum(agged.data1$Zone3)
sum(agged.data1$Zone4)
sum(agged.data1$Zone5)
sum(agged.data1$Zone6)

mean(zone1inc_F2$Income)
mean(zone2inc_F2$Income)
mean(zone3inc_F2$Income)
mean(zone4inc_F2$Income)
mean(zone5inc_F2$Income)
mean(zone6inc_F2$Income)
```


```{r}
all_arrests.model<-lm(Arrest~Zone2+Zone3+Zone4+Zone5+Zone6+Year, agged.data1)
summary(all_arrests.model)
```


```{r}
zone1.byDate<-crimeData%>%filter(INCIDENTZONE==1)

agged.sum.data1<-aggregate(cbind(Black, White, Other, Arrest, ViolentCrime)~date, data=crimeData, sum)
agged.mean.data1<-aggregate(cbind(Black, White, Other, Minor,YA,MA,Elderly, ViolentCrime)~date, data=crimeData, mean)
agged.data1<-merge(agged.mean.data1, agged.sum.data1, by="date")
agged.data1$Year<-year(agged.data1$date)
agged.data1$Month<-month(agged.data1$date)
agged.data1$wday<-wday(agged.data1$date, label=TRUE)
agged.data1$Zone<-1

Zones.df<-agged.data1

for(i in 2:6){
  zone.byDate<-crimeData%>%filter(INCIDENTZONE==i)
  
  agged.sum.data1<-aggregate(cbind(Black, White, Other, Arrest, ViolentCrime)~date, data=crimeData, sum)
  agged.mean.data1<-aggregate(cbind(Black, White, Other, Minor,YA,MA,Elderly, ViolentCrime)~date, data=crimeData, mean)
  agged.dataX<-merge(agged.mean.data1, agged.sum.data1, by="date")
  agged.dataX$Year<-year(agged.dataX$date)
  agged.dataX$Month<-month(agged.dataX$date)
  agged.dataX$wday<-wday(agged.dataX$date, label=TRUE)
  
  agged.dataX$Zone<-i
  
  Zones.df<-rbind(Zones.df, agged.dataX)
}

Zones.df
```
```{r}

crimeData$zone_inc<-NA
crimeData$zone_inc[crimeData$INCIDENTZONE==1]<-mean(zone1inc_F2$Income)
crimeData$zone_inc[crimeData$INCIDENTZONE==2]<-mean(zone2inc_F2$Income)
crimeData$zone_inc[crimeData$INCIDENTZONE==3]<-mean(zone3inc_F2$Income)
crimeData$zone_inc[crimeData$INCIDENTZONE==4]<-mean(zone4inc_F2$Income)
crimeData$zone_inc[crimeData$INCIDENTZONE==5]<-mean(zone5inc_F2$Income)
crimeData$zone_inc[crimeData$INCIDENTZONE==6]<-mean(zone6inc_F2$Income)

```

```{r}
mean_inc
```


```{r}
samp<-sample_n(agged.data1, 800)
ggplot(samp,aes(x=date, y=ViolentCrime.x))+geom_point()+geom_smooth(method="lm")+ ylim(0,.7)
```

```{r}
vi.arrests.byZone<-aggregate(ViolentCrime~INCIDENTZONE, crimeData, sum)
vi.arrests.byZone$scaled_vc<-  vi.arrests.byZone$ViolentCrime/mean_pop
vi.arrests.byZone
```


```{r}
crimeData$Month<-month(crimeData$date)
crimeData$spring<-ifelse(crimeData$Month>=3&crimeData$Month<=5,1,0)
crimeData$summer<-ifelse(crimeData$Month>=6&crimeData$Month<=8,1,0)
crimeData$fall<-ifelse(crimeData$Month>=9&crimeData$Month<=11,1,0)
crimeData$winter<-ifelse(crimeData$Month>=12|crimeData$Month<=2,1,0)

violent_arrests.model<-lm(ViolentCrime~as.character(INCIDENTZONE)+Year+winter+fall+spring+White, crimeData)
summary(violent_arrests.model)
```
```{r}
summary(violent_arrests.model)$coefficients[,"Std. Error"]
```

```{r}
ses<-summary(violent_arrests.model)$coefficients[,"Std. Error"]
stargazer(violent_arrests.model, ci=TRUE,ci.level=0.95, notes = "Intervals Below Coefficients are 95% Confidence Intervals",type="text")
```


```{r}
stargazer(violent_arrests.model, dep.var.labels="Proportion of Violent-Crime Arrests",covariate.labels=c("Zone 2", "Zone 3", "Zone 4", "Zone 5", "Zone 6", "OSC", "Year", "Winter","Fall", "Spring", "White" ), ci=TRUE,ci.level=0.95, notes = "Intervals Below Coefficients are 95% Confidence Intervals", type="html")
```


```{r}
gdp.crime<-aggregate(cbind(Arrest, ViolentCrime)~Date, data=crimeData, sum)
gdp.crime<-merge(gdp.crime, fred, by="Date")

gdp.crime$Year<-year(gdp.crime$Date)
gdp.crime$Month<-month(gdp.crime$Date)


gdp.crime$spring<-ifelse(gdp.crime$Month>=3&gdp.crime$Month<=5,1,0)
gdp.crime$summer<-ifelse(gdp.crime$Month>=6&gdp.crime$Month<=8,1,0)
gdp.crime$fall<-ifelse(gdp.crime$Month>=9&gdp.crime$Month<=11,1,0)
gdp.crime$winter<-ifelse(gdp.crime$Month>=12|gdp.crime$Month<=2,1,0)

gdp.crime
```
```{r}
install.packages("mFilter")
library(mFilter)
```


```{r}
gdp.crime$log.gdp<-log(gdp.crime$GDP)

gdp.hp<-hpfilter(gdp.crime$log.gdp, freq = 6.25,type = "lambda")
cyc<-gdp.hp$cycle
trend<-gdp.hp$trend

cyc
trend

gdp.cor<-lm(Arrest~GDP+Year, gdp.crime)
summary(gdp.cor)
```

```{r}
ggplot(gdp.crime.int)+geom_line(aes(x=Date, y=GDP))
```


```{r}
gdp.crime.int<-merge(gdp.crime, int.rates, by="Date")

gdp.int.cor<-lm(Arrest~GDP+Year+rate, gdp.crime.int)
summary(gdp.int.cor)
```
```{r}
agged.data1
```


```{r}
crimeData$Zone1<-ifelse(crimeData$INCIDENTZONE==1,1,0)


community.engagement$Zone.Num<-as.numeric(word(community.engagement$ZONE,2))

community.engagement$Zone1<-ifelse(community.engagement$Zone.Num==1,1,0)
community.engagement$Zone2<-ifelse(community.engagement$Zone.Num==2,1,0)
community.engagement$Zone3<-ifelse(community.engagement$Zone.Num==3,1,0)
community.engagement$Zone4<-ifelse(community.engagement$Zone.Num==4,1,0)
community.engagement$Zone5<-ifelse(community.engagement$Zone.Num==5,1,0)
community.engagement$Zone6<-ifelse(community.engagement$Zone.Num==6,1,0)

community.engagement$date<-mdy(community.engagement$`Event Date`)

community.engagement$num<-1
```

```{r}
com.eng<-aggregate(cbind(Zone1, Zone2,Zone3,Zone4,Zone5,Zone6,num)~date, data=community.engagement, sum)
com.eng
```

```{r}
com.eng.crime<-merge(agged.data1,com.eng, all.x=TRUE)
com.eng.crime
```

```{r}
ggplot(agged.data1,aes(x=date, y=Arrest))+geom_point()+geom_smooth(method="lm")
```

